Universal Anonymous Signatures

### 2022-07-15 prism-backend/research/gsac/relationships.tex
Added a paragraph with real-world sample use cases. Fixed some todos.
Some deep syntax re-writing.

  \scalebox{0.95}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
        & \fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \pcif \attrs
          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
          \pcreturn 0 \nonumber \\
        & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq
          \pcif \attrs_1(\cred) = n+1 \land \dattrs \subseteq \attrs: \pcreturn 1;
          \pcelse \pcreturn 0 \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\usk,\scred,\msg) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \pcreturn
          (\dattrs(\cred),\ast) \nonumber \\
        & \feval^{\attrs}(\usk,\cred,\msg) \coloneqq \pcif \CCommit(\usk;0) \in
          \attrs: \pcreturn (\attrs(\cred),\ast);
          \pcelse \pcreturn (\bot,\bot) \nonumber \\
        & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq
          \pcreturn \pcreturn((\attrs_1(\cred),\dattrs(\cred)),\ast) \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.95}{
    \begin{minipage}[t]{0.5\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\yeval,\usk,\cred,\msg) \coloneqq 0 \nonumber \\        
        & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    attribute in \cred. $\ast$ means the output is ignored (in these examples,
    we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{\Sign-prv}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in
  $\CUASGen^{\Sign-prv}$, using $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in $\CUASGen^{\Sign-prv}$,
  restricting \finsp to be $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$. Note that this does not affect security, as long as
  $\isk \getr \AttrSpace$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a set of public keys from a publicly available list of issuers
  (users), i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$.
  Then, runs the $\langle \Obtain,\Issue \rangle$ protocol as in
  $\CUASGen^{\Sign-prv}$, acting both as user and as issuer, using
  $\fissue^{\sring}$ as issuance function, and $\attrs \gets \sring$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$, using $\feval^{\attrs}$ as sign evaluation function,
  using as credential for signing the credential obtained in the desired
  $\langle \Obtain,\Issue \rangle$ session and, as \opk, any previously
  registered \opk (i.e., such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sring,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$. Note that $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
  $\finsp=\finsp^0$.
\end{description}

@@

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though, and it does
not seem hard to move from one to the other \todo{check}. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\needcite.

>>>>

  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \textbf{Issuance functions:}
      \begin{align}
        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
        & \fissue^{\sring}(\usk,\attrs,\cdot) \coloneqq \pcif \attrs
          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1;
          \pcelse \pcreturn 0 \nonumber \\
        & \fissue^{l,\dattrs}(\usk,\attrs,(\cid,\cattrs)) \coloneqq
          \pcif \attrs_1 = l+1 \land \attrs \subseteq
          \lbrace \cattrs_i \rbrace_{i\in\dattrs}: \pcreturn 1;
          \pcelse \pcreturn 0 \nonumber
      \end{align}

      \textbf{Signature evaluation functions:}
      \begin{align}
        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
          \nonumber \\
        & \feval^{\sring}(\usk,(\cid,\attrs),\cdot)
          \coloneqq \pcif \CCommit(\usk;0) \in \attrs:
          \pcreturn (\attrs,\ast);
          \pcelse \pcreturn \bot \nonumber \\
        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
          \nonumber
      \end{align}
    \end{minipage}
  }
  \vspace*{1em}

  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \textbf{Open functions:}
      \begin{align}
        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
        & \finsp^{\upk}(\cdot,\usk,\cdot,\cdot) \coloneqq \CCommit(\usk;0)
          \nonumber
      \end{align}
    \end{minipage}
    \hspace*{5em}
    % \begin{minipage}[t]{0.47\textwidth}
    %   \begin{framed}
    %     $\attrs(\cred)$ returns all attributes in \cred \\
    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
    %     $\ast$ means the output is ignored \\
    %     $\bot$ means the function fails
    %   \end{framed}
    % \end{minipage}
  }
  \caption{Functions for the \CUASGen restrictions described next.
    For readability, we use ``$\cdot$'' to denote input arguments that are
    ignored; and ``$\ast$'' to denote output values that can be set to anything
    (but should be ignored). $\bot$ means the function fails.}
    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
    % fails.}
  \label{fig:func-restrictions}
\end{figure}

@@

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{\Sign-prv}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in
  $\CUASGen^{\Sign-prv}$, using $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in $\CUASGen^{\Sign-prv}$,
  restricting \finsp to be $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$. Note that this does not affect security, as long as
  $\isk \getr \AttrSpace$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a set of public keys from a publicly available list of issuers
  (users), i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$.
  Then, runs the $\langle \Obtain,\Issue \rangle$ protocol as in
  $\CUASGen^{\Sign-prv}$, acting both as user and as issuer, using
  $\fissue^{\sring}$ as issuance function, and $\attrs \gets \sring$.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$, using $\feval^{\sring}$ as sign evaluation function,
  using as credential for signing the credential obtained in the desired
  $\langle \Obtain,\Issue \rangle$ session and, as \opk, any previously
  registered \opk (i.e., such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sring,\sig,\yeval,\msg,\feval).$] As in
  $\CUASGen^{\Sign-prv}$. Note that $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
  $\finsp=\finsp^0$.
\end{description}

@@

There are some differences, though. On the one hand, our signature anonymity
property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
Their privacy-1 variant is the traditional anonymity property of group
signatures, in which the opener is honest and the adversary can call the opening
oracle except for challenge signatures. In their privacy-2 variant, the opener
is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
(getting ther \osk), but the challenge signatures must have been generated using
the key of an uncorrupted opener; still, \adv~can call the open oracle for
challenge signatures, as long as they have the same \yinsp value. We believe
that these differences are mostly of theoretical interest, though. In practice,
what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
in MPS) that has too much granularity in their ranges, will lead to a barely
private system. This is a known issue, for instance, in functional encryption
\needcite.
